European or American? A re-examination of the transatlantic influence over the IMF

### 2025-09-12 manuscript/manuscript.qmd
Major: fix 3rd limitation

Third, our analysis focuses exclusively on lending outcomes and does not examine other dimensions of IMF operations, such as surveillance, technical assistance, or institutional governance. European and American influence may manifest differently across these various functions. Similarly, our study does not address the effectiveness or appropriateness of the lending arrangements influenced by great power politics—a question that would require additional data on economic outcomes and counterfactual analysis.

>>>>

Third, in terms of scope, three clarifications are in order. Our analysis focuses exclusively on lending outcomes and does not examine other dimensions of IMF operations, such as surveillance, technical assistance, or institutional governance. European and American influence may well manifest differently across these functions. Second, the effectiveness of IMF policies is also beyond the scope of our analysis. A large body of literature already addresses this question, and its findings can be combined with ours to inform policy debates. Third, our approach is deliberately empirical and positivist, aimed at identifying systematic patterns of influence rather than assessing the *appropriateness* of IMF lending arrangements. Questions of legitimacy and normative evaluation, long central to debates about the Fund, are not the direct focus of this paper, though we recognise that our results have implications for these debates and welcome further normative interpretations.
